\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-23 chapters/0_abstract.tex
Last changes

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines \algname{}, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied. An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset. 
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied. An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset. 
\end{abstract}

### 2019-05-23 chapters/3_algorithm.tex
Last changes

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With cannot-link constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{\algname{}: generalized algorithm for signed graph partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
      % \State
      \Repeat
        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
        % \State
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
        % \State
        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
        %   \EndFor
        % \EndIf
        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        % \EndIf

@@

In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 3 of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

In the second variant, when \texttt{addCannotLinkConstraints=True}, Algorithm \ref{main_alg} also introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering. This variant 
selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig. \ref{subfig:with_constraints}). If the interaction is repulsive, then the two clusters are constrained. If it is attractive, then they are merged, provided that they were not already previously constrained. 
The algorithm stops when all the remaining clusters are constrained.
% The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
% The graph clustering algorithm we will present in Sec. \ref{sec:algorithm} is a bottom-up approach starting with each node assigned to its own cluster and iteratively merging clusters. During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge. 
% For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$. As an example, given the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
% \begin{equation}
%   \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
% \end{equation}
% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.

In Appendix \ref{sec:detailed_impl}, we comment on the algorithm computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l | c | c  c}
            % \toprule\toprule
            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} Linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

@@

@@

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage). They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints. In Appendix \ref{sec:appendix_abs_max} we prove that it can be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def. in Table \ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graphs agglomerative algorithms or been combined with cannot-link constraints.

>>>>

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With cannot-link constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{\algname{}: generalized algorithm for signed graph partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$ with each node in its own cluster
      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
      % \State
      \Repeat
        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
        % \State
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
        % \State
        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
        %   \EndFor
        % \EndIf
        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        % \EndIf

@@

In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm. \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters. The algorithm has two variants. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual by repulsive interactions (see iterations on toy graphs in block 3 of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

In the second variant, when \texttt{addCannotLinkConstraints=True}, Algorithm \ref{main_alg} also introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering. This variant 
selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig. \ref{subfig:with_constraints}). If the interaction is repulsive, then the two clusters are constrained and its members can never merge in subsequent steps. If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained. 
The algorithm terminates when all the remaining clusters are constrained.
% The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
% The graph clustering algorithm we will present in Sec. \ref{sec:algorithm} is a bottom-up approach starting with each node assigned to its own cluster and iteratively merging clusters. During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge. 
% For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$. As an example, given the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
% \begin{equation}
%   \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
% \end{equation}
% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.

In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.

@@

\begin{table*}[b]
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l | c | c  c}
            % \toprule\toprule
            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

@@

%TALK ABOUT TABLE 1 and wonderfully it sumarizes 
Our main contribution is the generalized algorithm for signed graph partitioning, short GASP, that encompasses several known and novel agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.

@@

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was pioneered in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage). The authors present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms approximating the multicut optimization problem.
The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints. In Appendix \ref{sec:appendix_abs_max} we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def. in Table \ref{tab:linkage-criteria}). We observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.

### 2019-05-23 chapters/5_experiments_cityscapes.tex
Last changes

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs. Max.}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\begin{figure}[t]
\centering
\begin{minipage}[b]{0.5\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[b]{0.46\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
\end{minipage}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\begin{figure}[t]
\centering
\begin{minipage}[b]{0.5\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[b]{0.46\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
\end{minipage}
\end{figure}

### 2019-05-23 chapters/5_experiments_compare_rules.tex
Last changes

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

>>>>

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

### 2019-05-23 chapters/5_experiments_intro.tex
Last changes

% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to direct neighboring pixels
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

>>>>

% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to immediately adjacent pixels
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
